Self Regulation Ontology Retest Analyses

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
added clean boot figures with trial info

@@

```{r warning=FALSE, message=FALSE}
task_trial_num = trial_num_info %>% 
  filter(task == "task") %>% 
  ungroup() %>% 
  select(-task)

@@

@@

```{r message=FALSE, warning=FALSE}
p4_t <- tmp %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30),
        axis.text.x = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

>>>>

Extract trial number info to add to boot plot instead of adding another table

@@

Boot plot for tasks with trial info

```{r warning=FALSE, message=FALSE}
p4_t <- tmp %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

task_trial_num = trial_num_info %>% 
  filter(task == "task") %>% 
  ungroup() %>% 
  select(-task)

@@

Boot plot for surveys with trial info

```{r}
p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

survey_trial_num = trial_num_info %>% 
  filter(task == "survey") %>% 
  ungroup() %>% 
  select(-task)

survey_trial_num_table = survey_trial_num %>%
  mutate(y_axis = rev(ggplot_build(p5_t)$layout$panel_params[[1]]$y.major)) %>%
  gather(key, value, -y_axis, -task_group) %>%
  ggplot(aes(key, factor(y_axis)))+
  geom_text(aes(label=value), size=14)+
  xlab("")+
  ylab("")+
  theme(axis.ticks=element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text.x = element_text(size=30))+
  scale_x_discrete(position = "top",
                   breaks=c("mean_num_all_trials", "num_measures"),
                   labels=c("Mean Num Trials", "Num Measures"))

boot_survey_plot = arrangeGrob(p5_t, survey_trial_num_table, nrow=1, widths = c(3,2))

ggsave('Survey_Boot_w_trialinfo.jpg', plot = boot_survey_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
```

@@

```{r message=FALSE, warning=FALSE}
